### 2008-12-05 doc/sec/Sec_paper.tex
Some content improvement, and reference for Sec doc

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-middleware authentication and single sign-on for ARC grid
middleware
\par}

@@

\ In order to make the access to Grids as simple as possible, security
is one of the most important challenges in production Grids, especially
when the Grid applications are across multiple administration domains
as well as across heterogeneous Grid middlewares, such as some widely
scaled eScience applications which needs to coordinate resources
sharing among collection of autonomous institutions with different Grid
middlewares running on these resources. In this paper, we describe the
security implementation and consideration in new version of Advanced
Resource Connector (ARC) middleware, where the above issues have been
exploited. The main goal of ARC implementation in terms of security is
to let the middleware be capable to \ interoperate with other Grid
middlewares by leveraging standard specifications. The key aspect of
the work we have done is to enhance the current proxy certificate based
delegation and authentication by utilizing the Security Assertion
Markup Languages (\textit{SAML}) single sign-on (SSO) profile,
WS-Security in order to achieve cross-domain authentication. \

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
Grids provides the technology for large scaled, cross domains
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[ref1]. The resources that contribute to the
VO could come from independent administrative domains, and even require
different security approaches for control the access to themselves. The
same heterogeneous situation even critically applies to users who need
to access the VO, because users holding one kind of credential could
need to travel through multiple resources with different security
approaches. To solve the above issues, the Grid middleware should
provide the following ability: The user which participates the VO
should be able to access data and resources without being required to
constantly do authentication at each resource or data; The VO should be
able to easily manage the privileges or memberships to the users, and
VO together with its resources should be able to easily manage the
authorization, given the condition that the resources are actually
owned by different administrative domains.

In grid community, Grid Security Infrastructure (GSI)[ref2] is the
\textit{de facto} standard about authentication and \ transport level
communication, which is builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment; and X.509 certificates is
required for both of the client and service sides in order to achieve
mutual authentication. X.509 certificates is issued by trusted third
party called certificate authorities (CA), and then CAs constitute
trust federation and guarantee two different X.509 certificates from
different CAs can accomplish authentication to each other. So if a user
would access grid system, he/she should own a X.509 certificate which
is issued by a CA that is trusted by other{\textquotesingle}s entity in
the GSI based grid system.

In terms of the virtual organization issues mentioned earlier, GSI and
some other related solutions like virtual organization management
service (VOMS) [ref3] has partly solved the them in some sense. The
identity delegation and X.509 proxy certificate initiated by GSI can
achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate, even if some local or remote
entities access access resources on behalf of this user. \ As the most
successful grid authorization model, VOMS adopts X.509 Attribute
Certificate[ref4]. Attribute certificate is signed by VOMS server and
then binded to proxy certificates by client, \ and attributes
certificate includes the VO memberships which is associated with the
proxy certificate{\textquotesingle}s identity. Essentially the
resources can make access control decision based on parsing the VO
membership attributes from the homogeneous attribute certificate.

\ \ \ \ The VO is essentially supposed to be able to provide resource
sharing capability with resources running under heterogeneous
systems/middlewares. This goal can be achieved using Web Service
Architecture (WSA). Therefore, the Web Service technology has been
converged into Grid computing middlewares. The Web Service technology
has been adopted by Globus toolkit, gLite, as well as the ARC.
Actually, utilizing Web Service technology and providing seamless
interoperability with other middlewares is one of the main goals of the
new version of ARC middleware.

Unfortunately, the existing grid security solutions such as GSI and VOMS
do not apply to Web Service \ based application very well due to the
following reasons:

\liststyleLii
\begin{itemize}
\item Firstly, the common implementation for Web Service does not
necessarily recognize and then properly verify and parse the
certificate, since comparing with usual X.509 certificate, proxy
certificate needs different treatment such as proxy path verification. 
\item Secondly, the X.509 Attribute Certificate has not been adopted by
any Web Service implementation at all. 
\item Thirdly, what is even worse is that the GSS API based confidential
communication has also not been adopted by Web Service implementation.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s representative (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
There is some effort to add GSI support to adapt to the strict security
requirement including GSI from grid middlewares, such as GSI plug-in
for gSOAP[ref6]. However, this kind of solution
doesn{\textquotesingle}t help the existing grid middlewares
interoperate with other common Web Service implementation. Instead, Web
Service implementations commonly use the WS-Security, Security
Assertion Markup Languages (SAML), and standard SSL/TLS as well as
standard X.509 certificate when considering security. \

\ \ \ \ Moreover, the current grid security solutions require each user
to possess a X.509 certificate. But the process to get a certificate
may take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could most normally
have some local community/institutional credentials such as
username/passwords to which users are more familiar. To enable users
use their own community credential instead of the X.509 certificate to
access grid is a promising solution to make the grid be more easily
accessible.

\ \ \ \ The above analysis shows that in order to achieve
interoperability and accessibility for user to access grid system, we
need to address the mismatch between the different security solutions
from different middlewares while keeping the changes as minimum as
possible and the benefits as much as possible; also need to address the
mismatch between user{\textquotesingle}s normal experience and
middleware requirement in order to ensure the access as simple as
possible.

\ \ The approach in the new version of ARC is to utilize the existing
Web Service standards, such as SAML and WS-Security, to achieve the
interoperability and accessibility without breaking existing grid
specific security protocols.

\ The rest of this paper is organized as follows: Section 2 shows the
ARC grid middleware, especially the architecture if the new version of
ARC. Section 3 describes the solution about cross-domain authentication
and single sign-on is presented, including a few solutions implemented
for bridging the mismatch in terms of authentication. Section 4
discusses the related research, and Section 5 concludes.

@@

ARC(Advanced Resource Connector) is an open source grid middleware
solution released under GPL licence. ARC middleware initially aimed at
developing a grid middleware which provides characteristics such as
self-organized, fault-tolerant, non-intrusive, easy-management [fgcs
ARC paper]. \ Now \ the classic version of ARC provides grid services
such as grid job submission and management, resource characterization,
resource aggregation and discovery, basic data management, integration
of grid security solution, etc. Classic ARC has been deployed and used
in production environment, and been one of the mainly deployed grid
middlewares in Europe.

The new generation of ARC is funded by KnowARC project, and based on the
functionality and capabilities of the classic ARC middleware, it aims
at implementing a service-oriented middleware which will provide higher
levels of resource and user abstracting through well-defined web
service interface [Design document] in order to provide
interoperability with other service-based grid middlewares, as well as
other Web Service compatible applications.

As the key part of the implementation of new ARC middleware, there is a
lightweight web service container called HED (Hosting Environment
Daemon) which provides a host place for various services in application
level, as well as a host place for a bunch of components to support
flexible, interoperatible, and efficient communication mechanism. The
whole design of the HED is built around the idea of flexibility and
modularity, which means for the developer, he can easily concentrate on
the application level Web Service implementation by only using the core
minimum amount of components if he only would do application level
development, or he can easily concentrate on the middleware level
implementation such as supporting another communication protocol or
implementing authentication mechanism by using the core minimum amount
of components and external dependencies; also for the deployer, he can
easily configure and deploy the middleware and application for
different kinds of requirements without being bothered to know much
about the implementation.

@@

\begin{center}
\includegraphics[width=4.0673in,height=3.1047in]{Secpaper-img1.png}
\end{center}
The architecture of the Host Environment Daemon is illustrated as Figure
1. In general, there are a few \ components called MCC (Message Chain
Components) which are in charge of processing different messages for
different protocol levels. For instance, as shown in the example
message flow, HTTP MCC will process secure socket stream from TLS MCC
to generate output HTTP message to SOAP MCC, and also process SOAP
documentation from SOAP MCC to generate HTTP message to TLS MCC.

Two examples of MCC components configuration in Figure 1 shows MCC are
configurable: real line shows SOAP over HTTPS (HTTP over TLS), while
dotted line shows SOAP directly over TCP. Service administrator can
configure the MCCs according to his requirement, such as the
interoperability requirement with the other part. For instance, the
later configuration is compatible to WSE (Web Services Enhancement for
.NET) {\textquotesingle}s SOAP message mechanism (see
WSE{\textquotesingle}s \textit{SoapSender} and \textit{SoapReceiver}).
Another configuration could be SOAP over HTTPG (HTTP over GSI) which
can be used to interoperate with some service based on HTTPG such as
SRM (Storage Resource Manager) [ref] service. The easily configurable
characteristics shows the flexibility of HED in terms of protocol
supporting.

Because in the current state HED mostly provides modules for building
SOAP based Web Services, it is easy to think that HED is just another
Web Services development framework like Axis, gSOAP, XFire or any other
out of the numerous implementations. Instead, the idea of HED is to
provide framework for gluing functionalities and not a
re-implementation of various standards. Effectively that means if
Apache httpd web server is considered by developers as necessary for
serving as front-end to services there could be plugin code written
which places Apache2 into a chain of other plugins of the HED, the same
for the Apache Axis SOAP implementation, as shown in Figure 1.

Even though the external solutions like Axis and Apache httpd can be
used for protocol supporting, \ two protocols are completely developed
in HED to support HTTP and SOAP in order to make the solution
lightweight and needed an implementation of those supported protocols
that is both simple and lightweight. However external solutions are
used whenever is appropriate - as in the case of TLS (openssl is used),
GridFTP (GridFTP API is used), LDAP and some other cases, this
principle applies to Axis and Apache httpd if we used the API from
those solution to implement the plugins for supporting SOAP and HTTP
protocol.

HED contains a framework for implementing and enforcing authentication
and authorization. Each Message Chain Component (MCC) or service has a
common interface for implementing various authentication and
authorization functionality. This functionality is implemented by using
pluggable and configurable components (plug-ins) called
\textit{SecHandler}. The \textit{SecHandler} components are C++ classes
and provide method for processing messages traveling through Message
Chains of the HED. Each MCC or Service \ usually implement two queues
of SecHandlers -- one for incoming messages and one for outgoing called
{\textquotedblleft}incoming{\textquotedblright} and
{\textquotedblleft}outgoing{\textquotedblright} respectively. All
\textit{SecHandler} components attached to the queue are executed
sequentially. If any of them fails, message processing fails as well.
In figure 1, the {\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-module inside MCCs and
Services are examples of \textit{SecHandler}.

As explained above, HED is supposed to act as a service holder, but on
the client side, from implementation perspective, there is similar
architecture implemented for processing messages from different
protocols and handling security functionality, also there is a specific
application programming interface (API) for developers to easily write
Web Service client code to service.

@@

{\centering
3. Cross-domain authentication and Single Sign-On
\par}

For cross domain authentication, our work comprises the following five
major aspects:

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standardized community authentication from Shibboleth
Identity Provider software when users authenticate against Grid
services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication
\end{itemize}

\ \ 3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

AAI (Authentication and authorization Infrastructure) is a solution for
the authentication and authorization for inter-organization resource
sharing, such as electronic resource sharing between libraries, etc.
AAI implicitly applies to community/institutional/organization based
authentication where users are from different home communities but need
to get resources from other communities by using some federation
mechanism. Unlike the X.509 based authentication solution in current
grid systems, AAI does not require user to provide X.509 certificate,
instead, it can support different types of authentication, such as
username/password based authentication, IP address based
authentication, etc. There are a few implementations about AAI, among
which Shibboleth [ref] is one implementation which has been widely
deployed.

Shibboleth provides cross-domain single sign-on and attribute-based
authorization while preserving user privacy. Shibboleth is based on the
OASIS Security Assertion Markup Language (SAML), especially the \ new
version of Shibboleth supports SAML 2.0 specification. For
authentication, the main SAML profile that Shibboleth implements is the
SAML2.0 web browser SSO profile, which \ define two functional
components, an Identity Provider and a Service Provider. The Identity
Provider (IdP) is responsible for creating, maintaining, and managing
user identity, while the Service Provider (SP) is responsible for
controlling access to services and resources by using the SAML
assertion produced and issued by IdP upon request. In order to discover
which home community does a user from, Shibboleth specifies an optional
third component called {\textquotedblleft}Where Are You
From?{\textquotedblright} (WAYF) service to aid in the process of IdP
discovery, and this IdP discovery process is also standardized and
\ defined in SAML 2.0 specification and called as
{\textquotedblleft}Identity Profile Discovery
Profile{\textquotedblright}.

>>>>

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% Text styles
\newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
\newcommand\textstyleCitation[1]{\textit{#1}}
% List styles
\newcommand\liststyleLi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{${\bullet}$}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{${\bullet}$}
}
\newcommand\liststyleLiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleLv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.5in}
\setlength\paperheight{11in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.7874in}
\setlength\oddsidemargin{0.7874in}
\setlength\textheight{9.4251995in}
\setlength\textwidth{6.9251995in}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\begin{document}
{\centering
Towards cross-middleware authentication and single sign-on for ARC grid
middleware
\par}

@@

\ \ \ \ In order to make the access to Grids as simple as possible,
security is one of the most important challenges in production Grids,
especially when the Grid applications are across multiple
administration domains as well as across heterogeneous Grid
middlewares, such as some wide scale eScience applications which needs
to coordinate resources sharing among collection of autonomous
institutions with different Grid middlewares running on these
resources. In this paper, we describe the security implementation and
consideration in new version of Advanced Resource Connector (ARC)
middleware, where the heterogeneity issue have been exploited. The main
goal of ARC implementation in terms of security is to let the
middleware be capable of interoperating with other Grid middlewares by
leveraging standard specifications. The key aspect of the work we have
done is to enhance the current proxy certificate based authentication
and single sign-on by utilizing and enhancing the standardized Web
Service specifications such as Security Assertion Markup Languages
(\textit{SAML}) single sign-on (SSO) profile, Web Services Security in
order to achieve cross-middleware authentication and single sign-on.

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
\ \ \ \ Grids provides the technology for wide-scale, cross domains
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[1]. The resources that contribute to the VO
could come from independent administrative domains, and even require
different security approaches for control the access to themselves
because different middlerwares are used as platform. The same
heterogeneous situation even critically applies to users who need to
access the VO, because users holding one kind of credential could need
to travel through multiple resources with different security
approaches. To solve the above issues, the Grid middlewares should
provide the following ability: The user which participates the VO
should be able to access data and resources without being required to
constantly do authentication at each resource or data; The VO should be
able to easily manage the privileges or memberships to the users, and
VO together with its resources should be able to easily manage the
authorization, given the condition that the resources are owned by
different administrative domains.

\ \ \ \ In grid community, Grid Security Infrastructure (GSI)[2] is the
\textit{de facto} standard about authentication and \ transport level
communication, which builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment; and X.509 certificates is
required for both of the client and service sides in order to achieve
mutual authentication. X.509 certificates is issued by trusted third
party called certificate authorities (CA), and then CAs constitute
trust federation and guarantee two different X.509 certificates from
different CAs can accomplish authentication to each other. So in the
GSI based grid system, if a user would access grid system, he/she
should own a X.509 certificate which is issued by a CA that is trusted
by other entity.

\ \ \ \ In terms of the virtual organization issues mentioned earlier,
GSI and some other related solutions like virtual organization
management service (VOMS) [3] have partly solved the them in some
sense. The identity delegation and X.509 proxy certificate initiated by
GSI can achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate. \ As the most successful grid
authorization model, VOMS adopts Attribute Certificate[4]. Attribute
certificate is signed by VOMS server and then binded to proxy
certificates by client, \ and attributes certificate includes the VO
memberships which is associated with the proxy
certificate{\textquotesingle}s identity. Eventually the resources can
make access control decision based on parsing the VO membership
attributes from the homogeneous attribute certificate.

\ \ \ \ The VO is essentially supposed to be able to provide resource
sharing capability with resources running under heterogeneous
systems/middlewares. This goal can be achieved using Web Service
Architecture (WSA). Therefore, the Web Service technology has been
converged into Grid computing middlewares. The Web Service technology
has been adopted by Globus toolkit[5], gLite[6], as well as \ Advanced
Resource Connector(ARC) [7]. In fact, utilizing Web Service technology
and providing seamless interoperability with other middlewares is one
of the main goals of the new version of ARC middleware.

\ \ \ Unfortunately, the existing grid security solutions such as GSI
and VOMS do not apply to Web Service \ based application very well due
to the following reasons:

\liststyleLii
\begin{itemize}
\item Firstly, \ the GSS API based confidential communication has also
not been adopted by Web Service implementation.
\item Secondly, \ Attribute Certificate has not been adopted by any Web
Service implementation at all.
\item Thirdly, Web Service implementations commonly use the Web Services
Security(WS-Security)[8], Security Assertion Markup Languages
(SAML)[9], and standard SSL/TLS as well as standard X.509 certificate
when considering security, which make them impossible to interoperate
with the GSI based grid middlewares.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s delegatee (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
\ \ \ \ Moreover, the current grid security solutions require each user
to possess a X.509 certificate. But the process to get a certificate
may take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could most normally
have some local community/institutional credentials such as
username/passwords to which users are more familiar. To enable users to
use their own community credential instead of the X.509 certificate to
access grid is a promising solution to make the grid be more easily
accessible.

\ \ \ \ The above analysis shows that in order to achieve
interoperability and accessibility for user to access grid system which
is established on different middlewares, we need to address the
mismatch between the different security solutions from these
middlewares in order to ensure the interoperability as wide as
possible; also need to address the mismatch between
user{\textquotesingle}s normal experience and
middleware{\textquotesingle}s requirement in order to ensure the access
as simple as possible.

\ \ \ \ The approach in the new version of ARC is to utilize the
existing Web Service standards, such as SAML and WS-Security, to
achieve the interoperability and accessibility without breaking
existing grid specific security protocols.

\ \ \ \ The rest of this paper is organized as follows: Section 2 shows
the ARC grid middleware, especially the architecture of the new version
of ARC. Section 3 describes the consideration and implementation about
cross-middleware authentication and single sign-on is presented,
including a few solutions implemented for bridging the mismatch in
terms of authentication and single sign-on. Section 4 discusses the
related research, and Section 5 concludes.

@@

\ \ \ \ ARC(Advanced Resource Connector) is an open source grid
middleware solution released under Apache license. ARC middleware
initially aimed at developing a grid middleware which provides
characteristics such as self-organized, fault-tolerant, non-intrusive,
easy-management [10]. \ Now \ the classic version of ARC provides grid
services such as grid job submission and management, resource
characterization, resource aggregation and discovery, basic data
management, integration of grid security solution, etc. Classic ARC has
been deployed and used in production environment, and been one of the
mainly deployed grid middlewares in Europe.

\ \ \ \ The new generation of ARC is based on the functionality and
capabilities of the classic ARC middleware, and it aims at implementing
a service-oriented middleware which will provide higher levels of
resource and user abstracting through well-defined web service
interface [11] in order to provide interoperability with other
service-based grid middlewares, as well as other Web Service compatible
applications.

\ \ \ \ As the key part of the implementation of new ARC middleware,
there is a lightweight Web Service container called Hosting Environment
Daemon (HED) which provides a host place for various services in
application level, as well as a host place for a bunch of modules to
support flexible, interoperatible, and efficient communication
mechanism for building SOAP based Web Services. The whole design of the
HED is built around the idea of flexibility and modularity, which means
for the developer, he can easily concentrate on the application level
Web Service implementation by only using the core minimum amount of
components if he only would do application level development, or he can
easily concentrate on the middleware level implementation such as
supporting another communication protocol or implementing
authentication mechanism by using the core minimum amount of components
and external dependencies; also for the deployer, he can easily
configure and deploy the middleware and application for different kinds
of requirements without being bothered to know much about the
implementation.

@@

\begin{center}
\includegraphics[width=4.0673in,height=3.1047in]{Secpaper-img1.png}
\end{center}
\ \ \ \ The architecture of the HED is illustrated as Figure 1. In
general, there are a few \ components called Message Chain Component
(MCC) which are in charge of processing different messages for
different protocol levels. For instance, as shown in the example
message flow, HTTP MCC will process secure socket stream from TLS MCC
to generate output HTTP message to SOAP MCC, and also process SOAP
documentation from SOAP MCC to generate HTTP message to TLS MCC.

\ \ \ \ Two examples of MCC components configuration in Figure 1 shows
MCC are flexibly configurable: real line shows SOAP over HTTPS (HTTP
over TLS), while dotted line shows SOAP directly over TCP. Service
administrator can configure the MCCs according to the interoperability
requirement with the other part. For instance, the later example
configuration is compatible to WSE (Web Services Enhancement for .NET)
{\textquotesingle}s SOAP message mechanism (see WSE{\textquotesingle}s
\textit{SoapSender} and \textit{SoapReceiver}). Another configuration
could be SOAP over HTTPG (HTTP over GSI) which can be used to
interoperate with some service based on HTTPG such as Storage Resource
Manager (SRM)[12] \ service. The easily configurable characteristics
shows the flexibility of HED in terms of protocol supporting.

\ \ \ \ HED contains a framework for implementing and enforcing
authentication and authorization. Each MCC or Service has a common
interface for implementing various authentication and authorization
functionality. Each functionality can be implemented as a pluggable and
configurable component (plug-ins) called \textit{SecHandler} which is
C++ class and provides method for processing message that travels
through MCC or Service. Each MCC or Service is usually configured with
two queues of \textit{SecHandler} -- one for incoming message and one
for outgoing message respectively. All \textit{SecHandler} components
attached to the queue are executed sequentially. If any of them fails,
message processing fails as well. In Figure 1, the
{\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-module inside MCCs and
Services are examples of \textit{SecHandler}.

As explained above, HED is supposed to act as a Web/Grid Service
container, but on the client side, from implementation perspective,
there is similar architecture implemented for processing messages from
different protocols and handling security functionality, also there is
a specific application programming interface (API) for developers to
easily write Web Service client code.

@@

{\centering
3. Cross-middleware authentication and Single Sign-On
\par}

\ \ \ \ We exploited the authentication and single sign-on issue in the
scenario that user or user{\textquotesingle}s delegatee (act on behalf
of this user) needs to access across different middlewares. Our work
comprises the following five major aspects:

\liststyleLiii
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standard-compatible community authentication mechanism from
Shibboleth [13] Identity Provider software when users authenticate
against Grid services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificate for user by using the community
authentication, in order to interoperate with services that depends on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication.
\end{itemize}
3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

\ \ \ \ AAI (Authentication and authorization Infrastructure) is a
solution for the authentication and authorization for
inter-organization resource sharing, such as electronic resource
sharing between libraries, etc. AAI implicitly applies to community or
institutional based authentication where users are from different home
communities but need to get resources from other communities by using
some federation mechanism. Unlike the X.509 based authentication
solution in current grid systems, AAI does not require user to provide
X.509 certificate, instead, it can support different types of
authentication, such as username/password authentication, IP address
authentication, etc. There are a few implementations about AAI, among
which Shibboleth is one implementation which has been widely deployed.

\ \ \ \ Shibboleth provides cross-domain single sign-on and
attribute-based authorization while preserving user privacy. It is
based on the OASIS Security Assertion Markup Language (SAML),
especially the \ new version of Shibboleth supports SAML 2.0
specification. For authentication, the main SAML profile that
Shibboleth implements is the SAML2.0 web browser SSO profile, which
\ define two functional components, an Identity Provider and a Service
Provider. The Identity Provider (IdP) is responsible for creating,
maintaining, and managing user identity, while the Service Provider
(SP) is responsible for controlling access to services and resources by
using the SAML assertion produced and issued by IdP upon request. In
order to discover which home community does a user from, Shibboleth
specifies an optional third component called {\textquotedblleft}Where
Are You From?{\textquotedblright} (WAYF) service to aid in the process
of IdP discovery, and this IdP discovery process is also standardized
and \ defined in SAML 2.0 specification and called as
{\textquotedblleft}Identity Profile Discovery
Profile{\textquotedblright}.

\ \ \ \ We utilized the SAML2.0 web browser SSO profile for the
authentication in ARC middleware. But since the SSO profile is
initially supposed to protect web applications and provide
authentication for web users, we implemented some external code on the
client and service side to integrate SSO profile. On the client side,
apart from the client interface for writing Web Service client, we
implemented the user agent functionality of web browser in order to
mimic its behavior, such as http redirection, cookie processing (In
fact, the implementation of user agent is also based on the client
interface of ARC, specifically, the https client interface, since the
client interface of ARC can support different protocols which are
incarnated by different MCC). Hence client developers who would use
SAML2.0 SSO profile should call the user agent interface and then the
Web Service client interface. On the service side, we implemented the
Service Provider functionality (based on the HTTP MCC configured
together with TLS MCC) which is called SP Service. For Identity
Provider, the Shibboleth IdP implementation is used.

\ \ \ \ Figure 2 shows the process of SAML2.0 SSO integrated in ARC
client and service.
